A Parallel General Purpose Multi-Objective Optimization Framework, with Application To Beam Dynamics

### 2018-07-18 paper/prab.tex
making small edits from Andreas
fix Kraus and remove felsim

\author{Andreas Adelmann}
\email{andreas.adelmann@psi.ch}
\author{A. Kolano}
\altaffiliation[Also at ]{
	University of Huddersfield, West Yorkshire, United Kingdom}

\affiliation{
	PSI, Villigen, Switzerland}%

\author{Y Ineichen}%
\altaffiliation[Also at ]{Department of Computer Science, ETH Zurich, Switzerland}%Lines break

@@

\author{C. Metzger-Kraus }
\affiliation{% 
	place holder \\
}%

@@

In this paper we applied the framework to reproduce the important and well
  known Ferrario matching condition for the \textsc{250 MeV injector}, a part of PSI's
  \textsc{SwissFEL} project.
The beam size and emittance optimization was successful and emittance damping
  is observed in the accelerating cavity.
Also, the influence of the number of slices employed by the envelope tracker
  with respect to convergence was investigated.
We found that the optimal slice number is around 400 for the problem addressed
  here, producing the best trade-off between computational cost and accuracy
  of the solution of the simulation.
Similarly, the gun and beam line time step was investigated confirming the
  convergence of the results.
This first study shows that the framework is ready to tackle problems arising
  in the domain of beam dynamics.

Interestingly, the computation of a good approximation of the Pareto front is
  already feasible on a small cluster using only a modest number of MPI
  processes.
For 1000 generations consisting of 2048 feasible and 8354 infeasible function
  evaluations (simulations) the optimizer needed $845$ minutes on the
  \textsc{Felsim} cluster on $16$ processes.
When we double the number of processes to $32$ (\textsc{Felsim} allows a
  maximum of $64$ processes per job) the runtime improves to $302$ minutes (2048
  accepted and 5426 infeasible individuals).
Notice that the runtime can vary due to the random nature of the process.
Nevertheless we see a reasonable speeduo when using more cores to solve the
  optimization problem. %and the parallel performance will be further evaluated
%  in a forthcoming publication.
%The number of individuals is the only limiting factor.

>>>>

\author{Y. Ineichen }
\affiliation{% 
	place holder 1
}%

\author{A. Adelmann}
\email{andreas.adelmann@psi.ch}
\author{A. Kolano}
\altaffiliation[Also at ]{
	University of Huddersfield, West Yorkshire, United Kingdom and  CERN, Genf}
\author{C. Metzger-Kraus}
\altaffiliation[Also at ]{AiF Projekt GmbH}
\affiliation{
	PSI, Villigen, Switzerland}%

@@

@@

In this paper we applied the framework to reproduce the important and well
  known Ferrario matching condition for the \textsc{250 MeV injector}, a part of PSI's
  \textsc{SwissFEL} project.
The beam size and emittance optimization was successful and emittance damping
  is observed in the accelerating cavity.
Also, the influence of the number of slices employed by the envelope tracker
  with respect to convergence was investigated.
We found that the optimal slice number is around 400 for the problem addressed
  here, producing the best trade-off between computational cost and accuracy
  of the solution of the simulation.
Similarly, the gun and beam line time step was investigated confirming the
  convergence of the results.

%This first study shows that the framework is ready to tackle problems arising
%  in the domain of beam dynamics.
%
%Interestingly, the computation of a good approximation of the Pareto front is
%  already feasible on a small cluster using only a modest number of MPI
%  processes.
%  
%For 1000 generations consisting of 2048 feasible and 8354 infeasible function
%  evaluations (simulations) the optimizer needed $845$ minutes on the
%  \textsc{Felsim} cluster on $16$ processes.
%
%When we double the number of processes to $32$ (\textsc{Felsim} allows a
%  maximum of $64$ processes per job) the runtime improves to $302$ minutes (2048
%  accepted and 5426 infeasible individuals).
%Notice that the runtime can vary due to the random nature of the process.
%Nevertheless we see a reasonable speeduo when using more cores to solve the
%  optimization problem. %and the parallel performance will be further evaluated
%  in a forthcoming publication.
%The number of individuals is the only limiting factor.
